---
title: "R BioInformatics and Bioconductor"
author: "Nino Moriaty"
output: html_notebook
---


# Tips: About the R notebook
Actually the working directory will be reset when the chunk is finished running. If you want to change the workspace for the code sections, you should use the knitr root.dir option in the setup chunk to change the working directory for notebook chunks.


# Installation
```{r}
# Common installation method for Bioconductor Packages
# BiocManager::install("affy")
# 

```


# Check the manual from Bioconductor
Tips: Then you will find the information of the package with a website browser.
```{r}
browseVignettes("affy")

```


# Packages for this notebook
```{r}
library(affy)

```


# Microarray Analysis-Affymetrix
# Read the Affymetrix data from CEL file
R: The CEL file will be read as AffyBatch type and You can view the data structure.
```{r}
# Preparation for the working space
## Set the data directory
setwd("/media/ninomoriaty/My Passport/2 作死日常/2 MSc/Semester 2/Functional Genomic Technologies/FGT-Course/Week3")

## Before read the files, you should remember to simply confirm them with getwd/ls/dir
dir()

# Read the Affymetrix data from CEL file
## Mt1-Read All files in the working directory
celAll <- ReadAffy()
celSelect <- ReadAffy("GSM272753.CEL")  # Mt1-Read Specified files in the given directory

## Mt2-Read files and create a new data object
test <- read.table("afile.txt", sep = "\t", header = TRUE, row.names = 1, as.is = TRUE)
celMat <- as.matrix(test)
# Create data object from existing data object 
exprset1 <- new("ExpressionSet", exprs = celMat)  # Build expression set with numerical data
ls()  # Check the objects in the current working space.

## Mt3-Just for example, you can load microarray data within `Biobase` package
data("sample.ExpressionSet")
mymatrix <- exprs(sample.ExpressionSet)  # Extract a numerical matrix
mymatrix[1:10, ]
mynames <- sampleNames(sample.ExpressionSet)  # Extract sample names
mynames

```


```{r}

iris
```


# Normalise the with RMA or MAS-5
R: The AffyBatch type will be converted to ExpressSet type and the data (TODO: Understand the principles for the information and ).
```{r}

```





