---
title: "Preparing the results"
author: "Nino Moriaty"
output: html_notebook
---


# Graphic Output
Tips: Graphic Collector, the plotting scripts should be placed behind these commands.
```{r}
bmp("filename.bmp") # BMP file
jpeg("filename.jpg") # JPEG file
pdf("filename.pdf") # PDF file
png("filename.png") # PNG file
postscript("filename.ps") # PostScript file
svg("filename.svg") # SVG file
win.metafile("filename.wmf") # Windows metafile

# Return Output to Terminal
dev.off()

```



# Redirect the Output to files 
Tips: Somehow similar to the Shell I/O Redirection, it means that ALL outputs would be directed to your option until you turn off it. It could be considered as a collector of results and that's why it could collect the results/functions/scripts behind it.
```{r}
# Text Output
sink(file = "fliename") # overwritten, 
sink(file = "filename", append=TRUE) # append in the same file
sink(file = "filename", split=TRUE) # send the output to the screen and file
sink() # return the results to the screen

```






























