---
title: "R Visualising the data"
author: "Nino Moriaty"
output: html_notebook
---

# Pcp-Visualisation and usage
- This notebook record multiple methods to generate different plot with general R visualisation packages

# Packages for visuallisation
```{r}
library(ggplot2)
library(gplots)
```
## ggplot2
**Ref**
-  ggplot2 is one project in the tidyverse: https://ggplot2.tidyverse.org/
**Cc/Ab**
- ggplot2 generates figures with the principle of layers
- 
yyyyuuyyy
## gplots
**Ref**
- R Docuemntation for gplots: https://www.rdocumentation.org/packages/gplots/versions/3.1.1
**Ab**
- gplots is not the same as ggplot or ggplot2, it is a 


# Scatter Plot
**Pcp**
- Scatter Plot shows the distribution of the data points 
- Thus, major attributes of scatter plot is the adjustment of data points.

## r-base plot method
Lk: Another method for scatter plot can be found in the `Generate a picture file with png or pdf format` section in this notebook.
```{r}
# Load data
spData <- as.matrix(mtcars)

# Select the row/column to represent the data points in (x, y)
plot(spData[, 'mpg'], spData[, 'hp'])

# Customise points
plot(spData[, 'mpg'], spData[, 'hp'], 
     col = 'red',  # Att: col means colors but not column as ususal in R
     pch = 12)  # The shape of the data point: Differ different data points from different sets of data
# TODO: How to change the size and the alpha of the points 

# Customise axis
plot(spData[, 'mpg'], spData[, 'hp'], xlab = "MPG", ylab = "HP")  # Customise the axis labels

# Pair data from each column against EVERY other column
spData[1:4, 1:4]
pairs(spData[1:4, 1:4])

```
## ggplot2 method
## gplots method

# Histogram/Barcharts
```{r}
# Load data


```


# 

# Generate a picture file with png or pdf format
```{r}
testplot <- c(0, 1, 2, 3)
png("pngtest.png")
plot(testplot, type="l", col="blue")
points(testplot, col="red")  # Another 
dev.off()
```
